Incentivizing Exploration By Heterogeneous Users

### 2018-07-04 Poster/poster.tex
edits to poster

%==Titel, date and authors of the poster=======================================
\title{Incentivizing Exploration By Heterogeneous Users}
\author{Bangrui Chen\footnotemark[1], Peter I. Frazier\footnotemark[1] \& David Kempe\footnotemark[2]}
\institute[ORIE]
          {\footnotemark[1] ORIE, Cornell University; \footnotemark[2] Department of Computer Science, USC}
\date{\today}
%
%==some usefull qm commands====================================================
%  |x>
\newcommand{\ket}[1]{\left\vert#1\right\rangle}
%  <x|
\newcommand{\bra}[1]{\left\langle#1\right\vert}
%  <x|y>
\newcommand{\braket}[2]{\left< #1 \vphantom{#2}\,
                        \right\vert\left.\!\vphantom{#1} #2 \right>}
%  <x|a|y>
\newcommand{\sandwich}[3]{\left< #1 \vphantom{#2 #3} \right|
                          #2 \left|\vphantom{#1 #2} #3 \right>}
%  d/dt
\newcommand{\ddt}{\frac{d}{dt}}
%  D/Dx
\newcommand{\pdd}[1]{\frac{\partial}{\partial#1}}
%  |x|
\newcommand{\abs}[1]{\left\vert#1\right\vert}
%  k_{x}
\newcommand{\kv}[1]{\mathbf{k}_{#1}}
%==============================================================================
%==the poster content==========================================================
%==============================================================================
\begin{document}
%--the poster is one beamer frame, so we have to start with:
\begin{frame}[t]
%--to seperate the poster in columns we can use the columns environment
\begin{columns}[t] % the [t] options aligns the columns content at the top
%--the left column-------------------------------------------------------------
\begin{column}{0.28\paperwidth}% the right size for a 3-column layout
%--abstract block--------------------------------------------------------------
\begin{alertblock}{Abstract}
\begin{itemize}[label=\textbullet]
\item We consider the problem of incentivizing exploration with heterogeneous agents. 
\item Under the assumption that each arm is preferred by at least a fraction $p > 0$ of agents, we propose an algorithm that achieves expected cumulative regret of $O(Ne^{2/p} + N \log^{3}(T))$, using expected cumulative payments of $O(N^{2}e^{2/p})$. 
\item If $p$ is known or the distribution over agent preferences is discrete, the exponential term $e^{2/p}$ can be replaced with suitable polynomials in $N$ and $1/p$. 
\item For discrete preferences, the regret’s dependence on T can be eliminated entirely, giving constant (depending only polynomially on N and 1/p) expected regret and payments.
%\item We give variance bounds of the Markov chain in terms of the proposed gap
\end{itemize}
\end{alertblock}
\vskip2ex
%--requirements block-----------------------------------------------------------

\begin{block}{Preliminaries}
\begin{itemize}[label=\textbullet]
\item In this problem, $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
\item Agents arrive sequentially with preference vector $\theta_t$ and choose arms to pull based on their own private and heterogeneous linear utility functions over attributes and the estimates of the arms’ attribute vectors $\hat{u}_{i,t}$, derived from observations of other agents’ past pulls. 
\item Agents are myopic and selfish and thus would choose the arm with maximum estimated utility, i.e. they will pull arm $i_t = \arg\max_{i}\{\theta_{t}\cdot \hat{u}_{i,t}\}$.
\item  A principal, knowing only the distribution from which agents’ preferences are drawn, but not the specific draws, can offer arm-specific incentive payments $c_{t,i}$ to encourage agents to explore underplayed arms. 
\item We define the regret at time $t$ as $r_t = (\max_{i} \theta_t \cdot u_i) - \theta_t \cdot u_{i_t}$ and payment $c_t = c_{t,i_t}$.
\item The principal seeks to minimize the total expected cumulative regret incurred by agents relative to their best arms, while also making a small expected cumulative payment.
\end{itemize}
\end{block}

@@

\textbf{Notations:}
\vspace{0.5cm}
\begin{itemize}[label=\textbullet]
\item Phase: Our algorithm divides time into \emph{phases} $s = 1, 2, 3, \ldots$. Phase $s$ starts when each arm has been pulled at least $s$ times. We use $m_{t,i}$ to denote the number of pulls for arm $i$ up to time $t$ and indicate the start time of phase $s$ by $t_s$. 
\item Payment-eligible: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$) if both of the following hold:
\begin{itemize}[label=\textbullet]
\item $i$ has been pulled at most $s$ times up to time $t$, i.e., $m_{t,i} \leq s$.
\item  The conditional probability of pulling arm $i$ is less than$1/\log(s)$ given the current estimates $\hat{u}_{t,i'}$ of the arms' attribute vectors.  
\end{itemize}
\end{itemize}

>>>>

%==Titel, date and authors of the poster=======================================
\title{Incentivizing Exploration By Heterogeneous Users}
\author{Bangrui Chen\footnotemark[1], Peter I. Frazier\footnotemark[1] \& David Kempe\footnotemark[2]}
\institute[ORIE]
          {\footnotemark[1] ORIE, Cornell University; \footnotemark[2] Department of Computer Science, USC}
\date{\today}
%
%==some usefull qm commands====================================================
%  |x>
\newcommand{\ket}[1]{\left\vert#1\right\rangle}
%  <x|
\newcommand{\bra}[1]{\left\langle#1\right\vert}
%  <x|y>
\newcommand{\braket}[2]{\left< #1 \vphantom{#2}\,
                        \right\vert\left.\!\vphantom{#1} #2 \right>}
%  <x|a|y>
\newcommand{\sandwich}[3]{\left< #1 \vphantom{#2 #3} \right|
                          #2 \left|\vphantom{#1 #2} #3 \right>}
%  d/dt
\newcommand{\ddt}{\frac{d}{dt}}
%  D/Dx
\newcommand{\pdd}[1]{\frac{\partial}{\partial#1}}
%  |x|
\newcommand{\abs}[1]{\left\vert#1\right\vert}
%  k_{x}
\newcommand{\kv}[1]{\mathbf{k}_{#1}}
%==============================================================================
%==the poster content==========================================================
%==============================================================================
\begin{document}
%--the poster is one beamer frame, so we have to start with:
\begin{frame}[t]
%--to seperate the poster in columns we can use the columns environment
\begin{columns}[t] % the [t] options aligns the columns content at the top
%--the left column-------------------------------------------------------------
\begin{column}{0.28\paperwidth}% the right size for a 3-column layout
%--abstract block--------------------------------------------------------------
\begin{alertblock}{Abstract}
\begin{itemize}[label=\textbullet]
\item We consider incentivizing exploration with heterogeneous agents. 
\item When each arm is preferred by at least a fraction $p > 0$ of agents, our algorithm achieves expected cumulative regret of $O(Ne^{2/p} + N \log^{3}(T))$ using expected cumulative payments of $O(N^{2}e^{2/p})$. 
\item If $p$ is known or the distribution over agent preferences is discrete, the exponential term $e^{2/p}$ can be replaced with polynomials in $N$ and $1/p$. 
\item For discrete preferences, the regret’s dependence on T can be eliminated, giving constant (depending only polynomially on N and 1/p) expected regret and payments.
%\item We give variance bounds of the Markov chain in terms of the proposed gap
\end{itemize}
\end{alertblock}
\vskip2ex
%--requirements block-----------------------------------------------------------

\begin{block}{Model}
\begin{itemize}[label=\textbullet]
\item $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
\item Agents arrive sequentially.
\item Agent $t$ sees estimates of the arms’ attribute vectors $\hat{u}_{i,t}$, which are averages of other agents’ past pulls. 
\item Agents have heterogeneous linear preferences over arm attributes.
\item Agent $t$ has preference vector $\theta_t$ drawn from a known distribution.
\item A principal knows only the distribution from which agents’ preferences are drawn but not the specific draws.
\item The principal can offer arm-specific incentive payments $c_{t,i}$ to encourage agents to explore underplayed arms. 
\item Agents are myopic and selfish and choose the arm with maximum estimated utility, $i_t = \arg\max_{i}\{\theta_{t}\cdot \hat{u}_{i,t} + c_{t,i_t}\}$.
\item The regret at time $t$ is $r_t = (\max_{i} \theta_t \cdot u_i) - \theta_t \cdot u_{i_t}$ and the payment is $c_t = c_{t,i_t}$.
\item The principal seeks to minimize the total expected cumulative regret while also making a small expected cumulative payment.
\end{itemize}
\end{block}

@@

\textbf{Notation:}
\vspace{0.5cm}
\begin{itemize}[label=\textbullet]
\item Phase: We divide time into \emph{phases} $s = 1, 2, 3, \ldots$. Phase $s$ starts when each arm has been pulled at least $s$ times. $m_{t,i}$ denotes the number of pulls for arm $i$ up to time $t$. The start time of phase $s$ is $t_s$. 
\item Payment-eligible: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$) if both of the following hold:
\begin{itemize}[label=\textbullet]
\item $i$ has been pulled at most $s$ times up to time $t$, i.e., $m_{t,i} \leq s$.
\item  The conditional probability of pulling arm $i$ is less than$1/\log(s)$ given the current estimates $\hat{u}_{t,i'}$ of the arms' attribute vectors.  
\end{itemize}
\end{itemize}
